# Homerwork 6th benchmarks #

This documents shows benchmarks of functions created for 6th homework of IPI PAN Advanced R course.

## Exercise 06.01 - mode
Mode is the most frequently occurring value in an integer vector

  * mode - Rcpp function
  * mode2 - function written in R for reference

```{r}
x<-as.integer(runif(100)*100)
microbenchmark(mode(x), mode2(x))
```
```{r}
x<-as.integer(runif(10000)*100)
microbenchmark(mode(x), mode2(x))
```
```{r}
x<-as.integer(runif(100000)*10000)
microbenchmark(mode(x), mode2(x))
```

As we can see, Rcp is faster than R, but difference is smaller and smaller when data size grows.

## Exercise 06.02 - simplify2array2
This function converts list into matrix if possible.

  * simplify2array2 - Rcpp function
  * simplify2array - function from R base

```{r}
L<-list()
for (i in 1:10) L[[i]]<-as.integer(runif(10)*100)
microbenchmark(simplify2array2(L), simplify2array(L))
```
```{r}
L<-list()
for (i in 1:100) L[[i]]<-as.integer(runif(100)*100)
microbenchmark(simplify2array2(L), simplify2array(L))
```
```{r}
L<-list()
for (i in 1:1000) L[[i]]<-as.integer(runif(1000)*100)
microbenchmark(simplify2array2(L), simplify2array(L))
```

For this function, Rcpp i faster only for small lists. For lists with about 10000 elements times are similar, for more elements base R function is faster. This happens because Rcpp solution is just iterating through vectors from beginning to end while R is optimized to operations on whole vector at the same time.

## Exercise 06.03 - ass
This function generates all possible assignments of survey participants.

  * ass - Rcpp function
  * ass2 - function written in R for reference

```{r}
microbenchmark(ass(1), ass2(1))
```
```{r}
microbenchmark(ass(2), ass2(2))
```
```{r}
microbenchmark(ass(3), ass2(3))
```

As we can see, Rcpp function is O(log(n)), while R function is O(n). This happens because this Rcpp function uses STL algorithm which is highly optimized, while R uses own permutation function written in R.

